### 2023-01-06 frontmatter/acknowledgements.tex
Make project run in VS Code
Fix name highlighting and update font

%!TEX root = ../Thesis.tex
\chapter{Acknowledgements}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

\vspace*{\fill}
\noindent \textit{The project was funded by Corti and Innovation Fund Denmark through an industrial PhD grant (no.\@ 0153-00167B).}

>>>>

%!TEX root = ../thesis.tex
\chapter[acknowledgements]{Acknowledgements}
First of all, I want to thank all my supervisors...

\vspace*{\fill}
\noindent \textit{The project was funded by Corti and Innovation Fund Denmark through industrial PhD grant no.\@ 0153-00167B).}

### 2023-01-06 prefrontmatter/colophon.tex
Make project run in VS Code
Fix name highlighting and update font

%!TEX root = ../Thesis.tex

@@

\vspace*{\fill}
% \vspace*{0.15\textheight}
\small\sffamily
\noindent
\textsc{\textbf{DTU Compute}}\\
\textsc{\textbf{Department of Applied Mathematics and Computer Science}}\\
\textsc{\textbf{Technical University of Denmark}}
\smallskip\\
Matematiktorvet, Building 303B\\
2800 Kongens Lyngby, Denmark\\
% Phone +45 4525 3031\\
compute@compute.dtu.dk\\
www.compute.dtu.dk
\bigskip\\
\noindent
\textsc{\textbf{Corti}}\\
\textsc{\textbf{Research Department}}
\smallskip\\
Store Strandstræde 21. 4.tv\\
1255 København K, Denmark\\
info@corti.ai\\
www.corti.ai\\

>>>>

%!TEX root = ../thesis.tex

@@

\vspace*{\fill}
% \vspace*{0.15\textheight}
\small\sffamily
\noindent
\textsc{\textbf{Technical University of Denmark}}\\
\textsc{\textbf{Department of Applied Mathematics and Computer Science}}
% \textsc{\textbf{DTU Compute}}
\smallskip\\
\href{https://goo.gl/maps/Dx6rNjGT9Ad5xKgZ6}{%
Richard Petersens Plads, Building 324\\
2800 Kongens Lyngby, Denmark}\\
% Phone +45 4525 3031\\
\href{mailto:compute@compute.dtu.dk}{compute@compute.dtu.dk}\\
\href{www.compute.dtu.dk}{www.compute.dtu.dk}
\bigskip\\
\noindent
\textsc{\textbf{Corti}}\\
\textsc{\textbf{Research Department}}
\smallskip\\
\href{https://goo.gl/maps/X7en4p8vaHkfVuyJ7}{%
Store Strandstræde 21. 4.tv\\
1255 København K, Denmark}\\
\href{mailto:info@corti.ai}{info@corti.ai}\\
\href{www.corti.ai}{www.corti.ai}\\
